A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-17 main.tex
Fix mistakes.

Signatures are sequences of pairs of a constant and its type or a type variable and its kind.
Because we adopted a \LLF like system, constants and type variables for base types are given in the signature $\Sigma$.

@@

A type is a type variable which are declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
A function type in ordinary type systems are omitted because it is an specialized case of a dependent type.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.

>>>>

Signatures are sequences of pairs of a constant and its type or a type variable and its kind.
Because we adopted a \LLF-like system, constants and type variables for base types are given in the signature $\Sigma$.

@@

A type is a type variable which is declared in the signature, a dependent type, a dependent type applied a term, a code type, or an $\alpha$-closed type.
A dependent type $\Pi x:\tau.\tau$ is a type depending on values such as a vector with its length.
A function type in ordinary type systems is omitted because it is a specialized case of a dependent type.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.
